Make any stupid plot you want

### 2021-04-15 draft/sections/scraps.tex
intro + background
figure overhaul

- [ ] (6) Evaluation: The method of evaluation to verify that the proposed solution delivers the stated benefits must be given.
        The best justifications explicitly discuss particular choices in the context of several possible alternatives.
        1. Case studies in the form of implementations (is this feasible) 
        2. Comparison w/ existing implementation

@@

>>>>

- [x] (6) Evaluation: The method of evaluation to verify that the proposed solution delivers the stated benefits must be given.
        The best justifications explicitly discuss particular choices in the context of several possible alternatives.
        1. Case studies in the form of implementations (is this feasible) 
        2. Comparison w/ existing implementation

@@

Associativitly means (a*b)*c = a*(b*c), as you know. Replace * with whatever binary operator you like. Same thing. Key one for CS/cat theory is when a, b, c are functions and * is composition. When you have something that seems like it always holds (like associativity does for function composition and most operations you can think of), it can be confusing because it is like .... why do you need to check this? it always has to be true.
It turns out that it isn't for some binary operators that can be useful but we just don't see unless we are making general statements.
But when you are proving something, it is important step in the proof.
Part of the fact that the composition of equivariant functions eg. \nu and Q is equivariant, relies on the associativity. It just seems so obvious that you don't notice it, but if things wheren't associative .... suddenly all kinds of equations you are writing down and moving parenthesis, would either NOT be true, or be much more complicated.
one way to write equivariance (for a group at least) as invariance is
g^-1*\nu(g*\tau) = \nu(\tau)
just imagine if order of operations between function call and g* mattered... it is hard because function composition IS associative but if it wasn't you couldn't just write that.
There is an algebra called the octonians which is NOT associative but has a more complicated function so you can relate a*(b*c) with (a*b)*c with a isomorphic map (just isn't equal). Every equation becomes a mess. So the bottom line is that in a definition or a proof you might have to whip out associativity, but most of the time it does "just hold". It is mentioned when needed, but it isn't a serious constrain like continutity or equivariance ... it mostly "just holds".

monoid -> set w/ associativity and identity

set = R, f: R->R, 
composotion of functions from a space to itself, is associative (\compo)
